### 2017-07-19 background.tex
several minor changes

Traditionally data enclaves are hosted privately using on-premise infrastructure. As 
such they often require significant upfront investment (e.g. physical infrastructure) and reoccurring costs 
from the personnel required to operate the infrastructure as well as develop and maintain custom software. 
They are also often limited in their ability to scale
compute capabilities in response to requirements. In many cases an on-premise data enclave is far from ideal
when considering distributed research teams, large-scale data anlaytics, and highly sporadic
usage patterns common in data science. Instead, cloud hosted data enclaves offer scalability,
democratize access to capabilities, and support distributed collaborations. 
 %terms of enabling anyone to host a secure data enclave and collaborate safely with a
%distributed set of peers.

\NAME is a data-enclave designed to enable computation over sensitive datasets
in a cost effective and secure manner. In prior work we've shown that \NAME offers
a scalable solution to match the compute needs of a distributed research network.
This model involved two classes of users: 1) the administrators who take on the role of managing
data, approving access, and handling the transfer of data onto the data stores; and 2) the analysts
who perform the role of analyzing and interrogating data via analyses pipelines.

>>>>

Traditionally data enclaves are hosted privately using on-premise infrastructure. As 
such they often require significant upfront investment (e.g. physical infrastructure) and recurring costs 
from the personnel required to operate the infrastructure as well as develop and maintain custom software. 
They are also often limited in their ability to scale
compute capabilities in response to requirements. In many cases an on-premise data enclave is far from ideal
when considering distributed research teams, large-scale data anlaytics, and highly sporadic
usage patterns common in data science. Instead, cloud hosted data enclaves offer scalability,
democratize access to capabilities, and support distributed collaborations. 
 %terms of enabling anyone to host a secure data enclave and collaborate safely with a
%distributed set of peers.

\NAME is a data-enclave designed to enable computation over sensitive datasets
in a cost effective and secure manner. In prior work we've shown that \NAME offers
a scalable solution to match the compute needs of a distributed research network.
This model involved two classes of users: 1) the administrators who take on the role of managing
data, approving access, and handling the transfer of data onto the data stores; and 2) the analysts
who are the consumers of data, performing the role of analyzing and interrogating data
via analysis pipelines.
